### 2021-11-08 docs/ms.tex
no clue why this is happening, and I think it's a UTF-8 thing

\title{\texttt{\{peacesciencer\}}: A User's Guide for Quantitative Peace Science in R\thanks{Replication files are available on the author's Github account (\url{https://github.com/svmiller/peacesciencer}). \textbf{Current version}: June 21, 2021; \textbf{Corresponding author}: \href{mailto:steven.v.miller@gmail.com}{\nolinkurl{steven.v.miller@gmail.com}}.}}
\author{true}
\date{}

@@

\title{\texttt{\{peacesciencer\}}: A User's Guide for Quantitative Peace Science in R\thanks{Replication files are available on the author's Github account (\url{https://github.com/svmiller/peacesciencer}). \textbf{Current version}: June 21, 2021; \textbf{Corresponding author}: \href{mailto:steven.v.miller@gmail.com}{\nolinkurl{steven.v.miller@gmail.com}}.}  }

@@

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Steven V. Miller (Clemson University)},
             pdfkeywords = {software, statistical analysis, peace science, reproducibility},
            pdftitle={\texttt{\{peacesciencer\}}: A User's Guide for Quantitative Peace Science in R},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\usepackage{longtable}
\usepackage{booktabs}
\LTcapwidth=.95\textwidth
\linespread{1.05}
\usepackage{hyperref}
\usepackage{setspace}
\let\BeginKnitrBlock\begin \let\EndKnitrBlock\end
\usepackage{colortbl}
\arrayrulecolor{black}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\begin{document}

@@

\caption{\label{tab:tab-dd}A "Dangerous Dyads" Analysis of Non-Directed Dyad-Years from \{peacesciencer\}}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8cm}c}
\toprule
\textbf{ } & \textbf{Model 1}\\
\midrule
Land Contiguity & 1.044*\\
 & (0.057)\\
Dyadic CINC Proportion (Lower/Higher) & 0.444*\\
 & (0.036)\\
CoW Major Power in Dyad & 0.145*\\
 & \vphantom{1} (0.058)\\
Defense Pact & -0.102+\\
 & (0.058)\\
Dyadic Democracy (Weak-Link) & -0.509*\\
 & (0.052)\\
Dyadic GDP per Capita (Weak-Link) & 0.262*\\
 & (0.050)\\
Dyadic Militarization (Minimum) & 0.267*\\
 & (0.023)\\
t & -0.148*\\
 & (0.005)\\
t\textasciicircum{}2 & 0.002*\\
 & \vphantom{1} (0.000)\\
t\textasciicircum{}3 & 0.000*\\
 & (0.000)\\
Intercept & -3.055*\\
 & (0.064)\\
\midrule
Num.Obs. & 106937\\
\bottomrule
\multicolumn{2}{l}{\textsuperscript{} + p $<$ 0.1, * p $<$ 0.05}\\
\end{tabular}
\end{table}

@@

\caption{\label{tab:tab-cw}A Civil Conflict Analysis of Gleditsch-Ward State-Years in \{peacesciencer\}}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8cm}cc}
\toprule
\textbf{ } & \textbf{All UCDP Conflicts} & \textbf{Wars Only}\\
\midrule
Population Size (Lagged) & 0.229* & 0.272*\\
 & (0.067) & (0.106)\\
Extended UDS Democracy Score (Lagged) & 0.257 & -0.085\\
 & (0.181) & (0.270)\\
Extended UDS Democracy Score\textasciicircum{}2 (Lagged) & -0.726* & -0.761*\\
 & (0.211) & (0.352)\\
\% Mountainous Terrain (Logged) & 0.055 & 0.342*\\
 & (0.067) & (0.112)\\
Ethnic Fractionalization & 0.442 & 0.333\\
 & (0.358) & (0.554)\\
Religious Fractionalization & -0.389 & -0.281\\
 & (0.402) & (0.593)\\
t & -0.074+ & -0.111*\\
 & (0.039) & (0.056)\\
t\textasciicircum{}2 & 0.004* & 0.005+\\
 & (0.002) & (0.003)\\
t\textasciicircum{}3 & 0.000* & 0.000+\\
 & (0.000) & (0.000)\\
Intercept & -5.097* & -6.590*\\
 & (1.351) & (2.084)\\
\midrule
Num.Obs. & 8192 & 8192\\
\bottomrule
\multicolumn{3}{l}{\textsuperscript{} + p $<$ 0.1, * p $<$ 0.05}\\
\end{tabular}
\end{table}

>>>>

\title{\texttt{\{peacesciencer\}}: An R Package for Quantitative Peace Science Research\thanks{Replication files are available on the author's Github account (\url{https://github.com/svmiller/peacesciencer}). \textbf{Current version}: November 08, 2021; \textbf{Corresponding author}: \href{mailto:steven.v.miller@gmail.com}{\nolinkurl{steven.v.miller@gmail.com}}.}}
\author{true}
\date{}

@@

\title{\texttt{\{peacesciencer\}}: An R Package for Quantitative Peace Science Research\thanks{Replication files are available on the author's Github account (\url{https://github.com/svmiller/peacesciencer}). \textbf{Current version}: November 08, 2021; \textbf{Corresponding author}: \href{mailto:steven.v.miller@gmail.com}{\nolinkurl{steven.v.miller@gmail.com}}.}  }

@@

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Steven V. Miller (Clemson University)},
             pdfkeywords = {software, statistical analysis, peace science, reproducibility},
            pdftitle={\texttt{\{peacesciencer\}}: An R Package for Quantitative Peace Science Research},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\usepackage{longtable}
\usepackage{booktabs}
\LTcapwidth=.95\textwidth
\linespread{1.05}
\usepackage{hyperref}
\usepackage{setspace}
\let\BeginKnitrBlock\begin \let\EndKnitrBlock\end
\usepackage{colortbl}
\arrayrulecolor{black}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{siunitx}
\newcolumntype{d}{S[input-symbols = ()]}

@@

% 
\begin{document}

@@

\caption{\label{tab:tab-dd}A "Dangerous Dyads" Analysis of Non-Directed Dyad-Years from \{peacesciencer\}}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8cm}c}
\toprule
\textbf{ } & \textbf{Model 1}\\
\midrule
Land Contiguity & \num{1.044}*\\
 & (\num{0.057})\\
Dyadic CINC Proportion (Lower/Higher) & \num{0.444}*\\
 & (\num{0.036})\\
CoW Major Power in Dyad & \num{0.145}*\\
 & \vphantom{1} (\num{0.058})\\
Defense Pact & \num{-0.102}+\\
 & (\num{0.058})\\
Dyadic Democracy (Weak-Link) & \num{-0.509}*\\
 & (\num{0.052})\\
Dyadic GDP per Capita (Weak-Link) & \num{0.262}*\\
 & (\num{0.050})\\
Dyadic Militarization (Minimum) & \num{0.267}*\\
 & (\num{0.023})\\
t & \num{-0.148}*\\
 & (\num{0.005})\\
t\textasciicircum2 & \num{0.002}*\\
 & \vphantom{1} (\num{0.000})\\
t\textasciicircum3 & \num{0.000}*\\
 & (\num{0.000})\\
Intercept & \num{-3.055}*\\
 & (\num{0.064})\\
\midrule
Num.Obs. & \num{106937}\\
\bottomrule
\multicolumn{2}{l}{\rule{0pt}{1em}+ p $<$ 0.1, * p $<$ 0.05}\\
\end{tabular}
\end{table}

@@

\caption{\label{tab:tab-cw}A Civil Conflict Analysis of Gleditsch-Ward State-Years in \{peacesciencer\}}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8cm}cc}
\toprule
\textbf{ } & \textbf{All UCDP Conflicts} & \textbf{Wars Only}\\
\midrule
Population Size (Lagged) & \num{0.229}* & \num{0.272}*\\
 & (\num{0.067}) & (\num{0.106})\\
Extended UDS Democracy Score (Lagged) & \num{0.257} & \num{-0.085}\\
 & (\num{0.181}) & (\num{0.270})\\
Extended UDS Democracy Score\textasciicircum2 (Lagged) & \num{-0.726}* & \num{-0.761}*\\
 & (\num{0.211}) & (\num{0.352})\\
\% Mountainous Terrain (Logged) & \num{0.055} & \num{0.342}*\\
 & (\num{0.067}) & (\num{0.112})\\
Ethnic Fractionalization & \num{0.442} & \num{0.333}\\
 & (\num{0.358}) & (\num{0.554})\\
Religious Fractionalization & \num{-0.389} & \num{-0.281}\\
 & (\num{0.402}) & (\num{0.593})\\
t & \num{-0.074}+ & \num{-0.111}*\\
 & (\num{0.039}) & (\num{0.056})\\
t\textasciicircum2 & \num{0.004}* & \num{0.005}+\\
 & (\num{0.002}) & (\num{0.003})\\
t\textasciicircum3 & \num{0.000}* & \num{0.000}+\\
 & (\num{0.000}) & (\num{0.000})\\
Intercept & \num{-5.097}* & \num{-6.590}*\\
 & (\num{1.351}) & (\num{2.084})\\
\midrule
Num.Obs. & \num{8192} & \num{8192}\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}+ p $<$ 0.1, * p $<$ 0.05}\\
\end{tabular}
\end{table}
